Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-14 doc/report/msc-report.tex
"The thesis is presented in three major sections: problem statement, theoretical solution and implementation details." - it's really not.
doc/report/msc-report.tex: * minor additions and placeholders.

The thesis is presented in three major sections: problem statement,
theoretical solution and implementation details.

@@

@@

\chapterquote{Some random quote might be suitable here.}{Per}
\section*{Introduction}

@@

\section{Summary}

@@

>>>>

@@

\subsection*{Last.fm}

% TODO: renskriv these thoughts.

Last.fm is an internet radio station focusing on content, being a musical
encyclopedia. The web site.

Last.fm lets users submit what music they listen to, called \textit{scrobbling}.

Radio streams to users.

The web site, radio streaming and submissions (scrobbling) generates gigabytes
of data every day.

@@

\chapterquote{Some random quote might be suitable here.}{Per}

@@

@@

Introduce the chapter here.
